\chapter{Result}\label{ch:E}
\hspace*{0.5cm} During the final results of our graduation project, we would like to highlight several aspects of this project. 
\begin{enumerate}
    \item \textbf{Developed components of the project or under the name of their functionality:} Within the framework of our project, a platform was created for the mutually beneficial exchange of skills between students and also a donation system, including functionality for registering new users, creating profiles, searching and viewing available skills, as well as functionality for participating in the QA system and crowdfunding and giving a rating to the questions is he good or not \cite{gitproject}. 
    \item \textbf{User interface \nameref{des}:} All screenshots and links below to the platform provided allow you to visually evaluate the design and functionality of the final project developed by us.
    \item \textbf{Evaluation of completed goals:} During our analysis of the results achieved during this semester, we can conclude that most of the goals set were successfully achieved. In particular, the platform has successfully implemented the main functions that ensure the exchange of mutually beneficial skills and support for students' projects.
    \item \textbf{Testing results \nameref{qa}:} Testing of the platform revealed several minor bugs that were successfully fixed before the final version of the project. Overall, the platform has shown stable operation and high performance. 
    \item \textbf{Comparison with similar platforms:} Conducting a comparative analysis with existing platforms that offer similar functionality helped to identify unique features and areas in which our platform is superior to others or requires further improvement, that is, we took 4 types of projects and implemented them in one site specifically for students.
    \item \textbf{Data Security and confidentiality:} Assessment of the security measures applied within the framework of the platform to protect user data and privacy, ensuring compliance with relevant rules and standards. 
    \item \textbf{Action Plan for the future:} Drawing up an action plan for further development and improvements based on feedback received, new industry trends and changing user needs and preferences. This may include features such as gamification elements, integration with external tools or services, and expansion to new demographic user groups or geographic regions \cite{chatgpt}.
\end{enumerate}