\chapter{Conclusion}\label{ch:concl}
\hspace*{0.5cm} The main and important goal of our graduation project was to create a modern website and IOS application, geared to students on a mutually beneficial exchange of skills through which students could find new acquaintances and get the new skills they want and crowdfunding. We started this project from scratch from January to May and strictly adhered to the regulations of the interested parties. From the very beginning of our project, we began to analyze the market and found the pain in which students do not find friends at universities, do not improve their communication skills, etc. By conducting surveys of the target audience, we tried to do everything possible to make our website and application for iOS understandable and valuable. The use of modern methodologies has greatly helped in this project management, compliance with strictly tight deadlines, and the provide of meetings. As a result, it helped us to place responsibilities between us, someone was in charge of design, someone was in charge of development, and so on. We also learned how to work in a team to support each other and motivate each other. With the difficulties we faced, it was bringing our project online since we had little experience with this problem, but we did not give up and achieved our goal. The most important thing when working on our project for us was teamwork, which will become one of the indispensable and significant skills in any other IT project, because it is very difficult for one to develop an IT project, we even say it is not possible, therefore it is very important to make new acquaintances and create new startup projects, as they say, and suddenly it will shoot.